---
title: "Emotion network"
author: "Ian Douglas"
date: "2/17/2021"
output: html_document
---
```{r, message=FALSE, warning=FALSE, results='hold'}
library(tidyverse)
library(EGAnet)
library(NetworkToolbox)
box_path = Sys.glob("~/Box/Research/covid19")
readRDS.box = function(file, ...) {readRDS(Sys.glob(file.path(box_path, file)), ...)}
saveRDS.box = function(object, file, ...) {saveRDS(object, file.path(box_path, file), ...)}
read_csv.box = function(file, ...) {read_csv(Sys.glob(file.path(box_path, file)), ...)}
write.csv.box = function(object, file, ...) {write.csv(object, file.path(box_path, file), ...)}
```

# Read in the data
```{r}
covid = readRDS.box('data/*/time1+time2_LongData.rds')
covid1 = covid %>% filter(timepoint == 1)
covid2 = covid %>% filter(timepoint == 2)
# Create and save in the global environment for reference a list of subjects who
# both time 1 and 2 data
overlapping_id = intersect(covid1$ID, covid2$ID)
# separate out the emotion variables
covid_emo.list = list('T1' = covid1, 
                     'T2' = covid2) %>%
  purrr::map(., ~{
  .x %>%
      dplyr::select(ID, timepoint, matches('emo\\.past\\.7\\.days\\.[[:alpha:]]+$')) %>%
      dplyr::select(-ends_with(c('Other','OtherText', 'None'))) %>%
      mutate(across(starts_with('emo.past.7.days.'), scale)) %>%
      rename_all(~sub('emo.past.7.days.', '', .)) %>%
      # drop the redundant timepoint variables
      dplyr::select(-timepoint) %>%
      # set ID to the rownames instead of being a column
      column_to_rownames('ID')
  })
```

# Emotional variables
- Note each model is only fit for the overlapping subjects
- No point otherwise, cos the people for whom we can calculate change over time \
are only the overlapping subjects
```{r}
d1 = covid_emo.list$T1 %>% filter(rownames(.) %in% overlapping_id) %>% remove_rownames
net1 = EGA(d1, model='glass', algorithm = 'walktrap')
net.loads(net1)
covid_emo_cluster.list = covid_emo.list %>%
  purrr::map(~{.x[rownames(.x) %in% overlapping_id, ]}) %>%
  purrr::map(EGA, model = 'glasso', algorithm = 'walktrap', plot.EGA=F)
```

# Collect the network scores and variables loaings in long data frames
```{r}
emo_loadings = covid_emo_cluster.list %>%
  purrr::map(net.loads) %>%
  imap_dfr()

```

```{r}

```

# Now a version treating the ordinal variables as continuous.
# Note that the higher numbers correspond to more endorsement of the emotion,
# irrespective of the valence.
```{r}
caspe.emo.ega.continuous = EGAnet::EGA(
  data = CaspeEmotional %>% select(-ID) %>% mutate_all(as.numeric),
  model = 'glasso', algorithm = 'louvain', plot.EGA = F
)
```
```{r}
net.scores(data= CaspeEmotional %>% select(-ID) %>% mutate_all(as.numeric),
           A = caspe.emo.ega.continuous)$std.scores
```

# View the network and loadings
```{r}
plot(caspe.emo.ega.continuous)
net.loads(caspe.emo.ega.continuous)
std.continuous.ldngs = net.loads(caspe.emo.ega.continuous)$std
```
# Standardized scores for participants
```{r}
std_network_scores.continuous = net.scores(ContinuousData, caspe.emo.ega.continuous)$std.scores
car::scatterplotMatrix(std_network_scores.continuous)
```

# For better interpretation, collect the loadings into a data frame
```{r}
loadings.continuous = net.loads(caspe.emo.ega.continuous)$std %>%
       rownames_to_column('Variable') %>%
       pivot_longer(-Variable, names_to = 'Cluster', values_to='Loading') %>%
       group_by(Cluster) %>%
       arrange(.by_group = TRUE, desc(abs(Loading)))
loadings.continuous
```



# Finally, a version with continuous variables, but dropping the questions
# asking them to retroactively report which emotions they felt *more* than before.
("Concurrent" emotion-sampling only)
```{r}
caspe.emoConcurrent.ega = EGAnet::EGA(
  data = CaspeEmotional %>% select(-ID, -starts_with('More')),
  model = 'glasso', algorithm = 'louvain', plot.EGA = F
)
plot(caspe.emoConcurrent.ega)
concurrent.loadings = net.loads(caspe.emoConcurrent.ega.continuous)$std
concurrent.ldngs.df = concurrent.loadings %>%
       rownames_to_column('Variable') %>%
       pivot_longer(-Variable, names_to = 'Cluster', values_to='Loading') %>%
       group_by(Cluster) %>%
       arrange(.by_group = TRUE, desc(abs(Loading)))
#view(concurrent.loadings)
```


```{r}
most_recent_mental_health = readRDS("../../../Data/Cleaned/EF_CAPE_FINAL.rds")
emotional.scores = data.frame(ID = CaspeEmotional$ID, 
                              Scores = net.scores(data= CaspeEmotional %>% 
                                                    select(-ID) %>% 
                                                    mutate_all(as.numeric),
                                                  A = caspe.emo.ega.continuous)$std.scores,
                              stringsAsFactors = F)
caspeOutcomes.plusEmotional = left_join(
  x = emotional.scores, 
  y = most_recent_mental_health %>%
    select(ID, ADHD),
  by = "ID")
```


```{r}
summary(lm(Scores.1 ~ ADHD, data = caspeOutcomes.plusEmotional))
```

```{r}
summary(lm(Scores.2 ~ ADHD, data = caspeOutcomes.plusEmotional))
```

```{r}
summary(lm(Scores.3 ~ ADHD, data = caspeOutcomes.plusEmotional))
```



