---
title: "Merging time 1 and 2 COVID surveys"
output: html_document
---
```{r}
library(tidyverse)
library(magrittr)
box_path = "~/Box/Research/covid19" # set this to the full path to covid19 on box
read.csv.box = function(.path)
{
  read.csv(Sys.glob(file.path(box_path, .path)), stringsAsFactors = F)
}
readRDS.box = function(.path)
{
  readRDS(Sys.glob(file.path(box_path, .path)))
}
```


# Read in the time 1 and time 2 data
```{r}
t1 = readRDS.box("data//Timepoint1/*Factorcoded.rds")
t2 = readRDS.box("data//Timepoint2/*Factorcoded.rds")
```


# Merge

1. We are simply going to start by use rbind() to create long data
2. For factors with the same names but different levels, we will just set the \
levels to be the union of the levels of both timepoints.

-First see how many names overlap
```{r}
length(intersect(names(t1), names(t2)))
```

There are 179 variables in common between the two datasets
```{r}
setdiff(names(t1), names(t2))
setdiff(names(t2), names(t1))
```


`sex`, `num_siblings`, & `school_closure_date` were only collected at time 1, but they are applicable \
to both timepoints, so we'll set them aside and merge them in later.

The 16 variables (8 at each time point) that start either with `soc.since.closure` or `soc.since.september` \
are in fact the same question, but are relative to events that were ~3 to 6 months prior (either start of covid, \
or start of what would have been the next school year at time). So these will be renamed, and the "since.closure." \
and "since.september" will be dropped from the variable names so they can be merged.

All other variables that don't have a match at the other timepoint, will be prepended "time{1,2}.".
```{r}
demographics = t1[c('ID', 'sex', 'num_siblings', 'school_closure_date')]
t1_only = names(t1)[!names(t1) %in% names(t2)] %>%
  {.[!. %in% names(demographics[-1])]} %>%
  Filter(x=., f=function(x) !grepl('since.closure', x))
t2_only = names(t2)[!names(t2) %in% names(t1)] %>%
  {.[!. %in% names(demographics[-1])]} %>%
  Filter(x=., f=function(x) !grepl('since.september', x))
# Rename these columns, and the ones mentioned in the comment above this chunk.
t1 %<>% rename_at(vars(all_of(t1_only)), ~paste('time1.', ., sep="")) %>%
  rename_at(vars(contains('since.closure.')), ~sub('since.closure.', '', .)) %>%
  # Additionally, drop the demographic columns that will be added back later
  select(-all_of(names(demographics[-1])))
t2 %<>% rename_at(vars(all_of(t2_only)), ~paste('time2.', ., sep="")) %>%
  rename_at(vars(contains('since.september.')), ~sub('since.september.', '', .))
```

-Check that renaming worked:
```{r}
setdiff(names(t1), names(t2))
setdiff(names(t2), names(t1))
```

# Final pre-merging step, create a new column in each data frame for the time points
```{r}
t1 %<>% mutate(timepoint = 1)
t2 %<>% mutate(timepoint = 2)
```

# Merging

1. Start by merging the columns shared by both
```{r}
shared_cols = intersect(names(t1), names(t2))
merge_intersection = rbind(t1[shared_cols], t2[shared_cols])
```

2. Bring in the unique columns
```{r}
t1_unique = t1 %>% select(-all_of(names(merge_intersection %>% select(-ID, -timepoint))))
t2_unique = t2 %>% select(-all_of(names(merge_intersection %>% select(-ID, -timepoint))))

merged_with_uniques = list(merge_intersection, t1_unique, t2_unique) %>%
  reduce(left_join, by = c('ID', 'timepoint'))
```

3. Add back the demographics, reorder columns
```{r}
all_merged = left_join(merged_with_uniques, demographics, by = 'ID') %>%
  select(-matches('^time[0-9]'), everything()) %>%
  select(ID, timepoint, timestamp, sex, age, num_siblings, 
         starts_with('school'), EnterEmailForAmazonGiftCardRaffle,
         everything())
```


# Save the result
```{r}
system('mkdir ~/Box/Research/covid19/data/Clean/')
saveRDS(all_merged, "~/Box/Research/covid19/data/Clean/time1+time2_LongData.rds")
```